Foreign Aid Choices and Effects

### 2022-09-26 Paper.tex
New thoughts on deglobalization

\documentclass{article}
\usepackage[utf8]{inputenc}
\title{Foreign Aid Choices and Effects}
\author{Nicholas Ray}
\date{September 2022}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools,amssymb,amsthm}
\usepackage{setspace}
\doublespacing
\usepackage[backend=biber, style=authoryear, maxbibnames=99]{biblatex}
\renewbibmacro{in:}{}
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}
  \setunit*{\addnbthinspace}
  \printfield{number}
  \setunit{\addcomma\space}
  \printfield{eid}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\AtEveryBibitem{
  \clearfield{issn}
  \clearfield{month}
  \clearfield{urlyear}
  \clearlist{language}
  \clearfield{note}
  \ifentrytype{online}{}{
    \clearfield{url}
  }
}
\addbibresource{References.bib}
\begin{document}
\maketitle
\section*{What needs to be explained} 
Developing countries seem to have an increased ability to choose donors for foreign aid. Not only has China been giving an incredible amount of aid, but now the U.S. and G7 are expanding their aid opportunities. Given this phenomenon, how do aid-seeking countries decide between bilateral donors and international institutions like the IMF and World Bank? And, how does choosing Chinese money over IMF funds, for instance, affect the politics of the recipient country? In other words, what is the political difference between receiving money from international organizations and other entities, like the U.S. or China? Is the BRI really an attractive substitute for IMF funding?

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\title{Foreign Aid Choices and Effects}
\author{Nicholas Ray}
\date{September 2022}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools,amssymb,amsthm}
\usepackage{setspace}
\doublespacing
\usepackage[backend=biber, style=authoryear, maxbibnames=99]{biblatex}
\renewbibmacro{in:}{}
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}
  \setunit*{\addnbthinspace}
  \printfield{number}
  \setunit{\addcomma\space}
  \printfield{eid}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\AtEveryBibitem{
  \clearfield{issn}
  \clearfield{month}
  \clearfield{urlyear}
  \clearlist{language}
  \clearfield{note}
  \ifentrytype{online}{}{
    \clearfield{url}
  }
}
\addbibresource{References.bib}
\begin{document}
\maketitle
\section*{What needs to be explained}
Given the seeming consensus of economic and political deglobalization,  namely in the West, there is attention being paid to China's position in this story, whether as a cause or of an effect. Regardless, I argue that China's eminence in the foreign aid spending decreases donor competition for foreign aid and leads to a reduction in perceived concessions on behalf of the recipient. Further, autocratic countries are likely to disproportionately benefit from this concession deficit and thus work more with China than democracies. Can I formalize this?
------

Developing countries seem to have an increased ability to choose donors for foreign aid. Not only has China been giving an incredible amount of aid, but now the U.S. and G7 are expanding their aid opportunities. Given this phenomenon, how do aid-seeking countries decide between bilateral donors and international institutions like the IMF and World Bank? And, how does choosing Chinese money over IMF funds, for instance, affect the politics of the recipient country? In other words, what is the political difference between receiving money from international organizations and other entities, like the U.S. or China? Is the BRI really an attractive substitute for IMF funding?
